Simultaneous segmentation and registration of diffusion MR images of the brain driven by active-contours

### 2015-02-19 Publications/2015-NeuroImage/04-methods.tex
minor updates

\paragraph*{Simulated phantoms}%
\label{sec:digital_phantoms}
We proved the concept on simplistic digital phantoms which we will name after their
  appearance as ``box'', ``ball'', ``L-shape'', and ``gyrus'' (\autoref{fig:phantom},
  boxes A and B).
Using \emph{phantomas} \citep{caruyer_phantomas_2014}, we simulated \gls*{t1} and
  \gls*{t2} images (TE/TR=10/1500ms and TE/TR=90/5000ms
  respectively) corresponding to each shape.
Simulations were conducted with rician noise for a \gls*{snr} of 300.0, and
  two image resolutions, $1.0mm$ and $2.0mm$, both isotropic.
The reference surfaces were extracted using the marching-cubes algorithm
  shipped with \emph{FreeSurfer} \citep{fischl_freesurfer_2012}
  at the higher resolution (1.0mm isotropic).

>>>>

\paragraph*{Simulated phantoms}%
\label{sec:digital_phantoms}
We proved the concept on simplistic digital phantoms which we will name after their
  appearance as ``box'', ``ball'', ``L-shape'', and ``gyrus'' (\autoref{fig:phantom},
  boxes A and B).
Using \emph{phantomas} \citep{caruyer_phantomas_2014}, we simulated
  \gls*{t1} (TE/TR=10/1500ms) and \gls*{t2} images (TE/TR=90/5000ms)
  corresponding to each appearance shape, with two resolutions each
  ($1.0mm$ and $2.0mm$ isotropic).
Simulations were corrupted with rician noise for a \gls*{snr} of 300.0.
The reference surfaces were extracted using the marching-cubes algorithm
  shipped with \emph{FreeSurfer} \citep{fischl_freesurfer_2012}
  at the higher resolution (1.0mm isotropic).

### 2015-02-19 Publications/2015-NeuroImage/05-results.tex
minor updates

\paragraph*{Assessing the segmentation model}\label{sec:res_model_and_metric} %
%
Preliminarly, we investigated the aptness of our segmentation model to play as cost function
  driving the registration process.
First, we selected the 6-regions model described in \nameref{sec:human_connectome} after
  visual evaluation of the joint distribution {\color{red} REF Supplemental} of several
  alternative models for segmenting the target bivariate images (\gls*{fa} and \gls*{adc}).
Since susceptibility-derived distortions are always aligned with the phase encoding axis
  and feature the property of being linear with respect to the phase inhomogeneity map,
  we reduced the dimensionality of the error space to one dimension.
Thus, the energy functional \eqref{eq:energy} was evaluated for the contour positions
  obtained along a lineralized space of distortions
  $\hat{U}\{\vec{r}\} = \epsilon \cdot U_{true} = \vec{r} + \epsilon \cdot u(\vec{r})$,
  with $\epsilon \in [-1.1, 1.1]$.
The result of this experiment is shown in \autoref{fig:realdata}.
The metric consistently displayed its minimum at the zero-error point.

>>>>

\paragraph*{Assessing the segmentation model}\label{sec:res_model_and_metric} %
%
Preliminarly, we investigated the aptness of our segmentation model to play as cost function
  driving the registration process.
First, we selected the 6-regions model described in \nameref{sec:human_connectome} after
  visual evaluation of the joint distribution {\color{red} REF Supplemental} of several
  alternative models for segmenting the target bivariate images (\gls*{fa} and \gls*{adc}).
Since susceptibility-derived distortions are always aligned with the phase encoding axis
  and feature the property of being linear with respect to the phase inhomogeneity map,
  we reduced the dimensionality of the error space to one dimension.
Thus, the energy functional \eqref{eq:energy} was evaluated for the contour positions
  obtained along a lineralized space of distortions
  $\hat{U}\{\vec{r}\} = \epsilon \cdot U_{true} = \vec{r} + \epsilon \cdot u(\vec{r})$,
  with $\epsilon \in [-1.1, 1.1]$.
The result of this experiment is shown in \autoref{fig:energymap}.
The metric consistently displayed its minimum at the zero-error point.

\begin{figure}
	\includegraphics[width=\linewidth]{figures/figure04.pdf}
	\caption{Assessment of the segmentation model, sampling the value of the energy functional
	\eqref{eq:energy} versus several registration errors generated as explained in
	\nameref{sec:res_model_and_metric}.
	The metric of our registration method displayed a smooth gradient towards the minimum
	located at the $\epsilon = 0.0$ point.}\label{fig:energymap}
\end{figure}
